\textbf{Towards File System integrity verification in BTRFS}

### 2019-08-02 paper.tex
Remove trailing whitespace.
use graph instead of tabular representation for algorithm performance

\section{Architecture}
\subsection{Preliminary Work}
After the initial rework of BTRFS' checksum handling was merged in Linux
Kernel version 5.3, a second patchset has been sent to add a second checksum
type XXHASH64\footnote{\href{http://www.xxhash.org}{http://www.xxhash.org}}
that was frequently requested by the community. XXHASH64 is no
cryptographically secure hash function but it can be used to ease
de-duplication of blocks and is generally considered a fast hash function. Table
~\ref{tab:hash-speed} holds performance data of Hash functions evaluated by
David Sterba in the course of this.
This patchset also included the necessary changes to BTRFS' user-space
utilities in order to create a File System with a different checksum algorithm
than the default CRC32C.

\begin{table}
	\centering
	\begin{tabular}{l | r | r } 
		Hash & Total Cycles & Cycles per Iteration \\	
		\hline
		CRC32C & 1783997556 & 1783 \\
		CRC32C\_SW & 1738434898 & 1738 \\
		XXHASH & 2501653700 & 2501 \\
		BLAKE2b-256-arch & 17754335778 & 17754 \\
		BLAKE2b-256 & 23867725764 & 23867 \\
		BLAKE2s-arch & 25877188085 & 25877 \\
		BLAKE2s & 34630837258 & 34630 \\
		SHA256 & 106150926755 & 106150 \\
		SHA3 & 289233228792 & 289233 \\
		\hline
	\end{tabular}
	\caption{Speedtest of different hash functions with 4096 byte blocks
	and 1,000,000 iterations}
	\label{tab:hash-speed}
\end{table}

>>>>

\section{Architecture}
\subsection{Preliminary Work}
After the initial rework of BTRFS' checksum handling was merged in Linux
Kernel version 5.3, a second patchset has been sent to add a second checksum
type XXHASH64\footnote{\href{http://www.xxhash.org}{http://www.xxhash.org}}
that was frequently requested by the community. XXHASH64 is no
cryptographically secure hash function but it can be used to ease
de-duplication of blocks and is generally considered a fast hash function. Table
~\ref{fig:hash-speed} holds performance data of Hash functions evaluated by
David Sterba in the course of this.
This patchset also included the necessary changes to BTRFS' user-space
utilities in order to create a File System with a different checksum algorithm
than the default CRC32C.

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{algo-perf-data.png}
	\caption{Speedtest of different hash functions with 4096 byte blocks
	and 1,000,000 iterations}
	\label{fig:hash-speed}
\end{figure}
